Service Chain Placement in SDNs\tnoteref{t1}

### 2019-03-13 src/chain.tex
fix bib

Lukovszki and Schmid~\cite{LukovszkiSchmid15} studied the problem of
admission control and placement of service chains, where each chain is
associated with a source-destination pair and is supposed to be routed
via an ordered sequence of $\ell$ VNFs.  The VNFs may have multiple
instantiations, but each node has a limited capacity that bounds the
number of requests it may service.
%
They presented an $O(\log \ell)$-competitive algorithm for the problem
of maximizing the number of serviced chains, assuming that capacities
are $\Omega(\log \ell)$.
%at least logarithmic in $\ell$.
It is also shown that this ratio is asymptotically optimal even for
randomized online algorithms.  APX-hardness results for the offline
version of the problem were also presented.
%
Rost and Schmid~\cite{RostSchmid16} considered variant of this
problem, where each node can host a subset of the VNFs.  In addition,
each VNF has a demand and each VNF-node pair has a capacity, and in a
feasible solution the total demand for each pair is bounded by the
capacity.  They considered two goals: maximum profit and minimum
resource cost and gave bicriteria approximation algorithms which are
based on LP-rounding for several special cases.
%
\fix{Sahhaf et al.~\cite{SAHHAF2015492} studied a generalization of the Virtual Network Embedding
Problem where each network function can be decomposed into multiple network function graphs.
They proposed two novel approaches to use service
decompositions at the time of service embedding (i) an
ILP-based algorithm that finds an optimal embedding and (ii) a heuristic-based algorithm to cop with the scalability issues of the first algorithm.}

@@

We note that cactus graphs were also considered in~\cite{FPS17}.

>>>>

Lukovszki and Schmid~\cite{LukovszkiSchmid15} studied the problem of
admission control and placement of service chains, where each chain is
associated with a source-destination pair and is supposed to be routed
via an ordered sequence of $\ell$ VNFs.  The VNFs may have multiple
instantiations, but each node has a limited capacity that bounds the
number of requests it may service.
%
They presented an $O(\log \ell)$-competitive algorithm for the problem
of maximizing the number of serviced chains, assuming that capacities
are $\Omega(\log \ell)$.
%at least logarithmic in $\ell$.
It is also shown that this ratio is asymptotically optimal even for
randomized online algorithms.  APX-hardness results for the offline
version of the problem were also presented.
%
Rost and Schmid~\cite{RostSchmid18} considered variant of this
problem, where each node can host a subset of the VNFs.  In addition,
each VNF has a demand and each VNF-node pair has a capacity, and in a
feasible solution the total demand for each pair is bounded by the
capacity.  They considered two goals: maximum profit and minimum
resource cost and gave bicriteria approximation algorithms which are
based on LP-rounding for several special cases.
%
\fix{Sahhaf et al.~\cite{SAHHAF2015492} studied a generalization of the Virtual Network Embedding
Problem where each network function can be decomposed into multiple network function graphs.
They proposed two novel approaches to use service
decompositions at the time of service embedding (i) an
ILP-based algorithm that finds an optimal embedding and (ii) a heuristic-based algorithm to cop with the scalability issues of the first algorithm.}

@@

We note that cactus graphs were also considered in~\cite{RostSchmid18}.
